---
output:
  pdf_document: 
    latex_engine: xelatex
    keep_tex: false
geometry: 
  - paperwidth=8.5in
  - paperheight=11in
  - margin=0.05in 
 
header-includes:
  \usepackage{fontspec}
  \setmainfont{Calibri}
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
  \graphicspath{{C:/Users/tdmed/OneDrive/_Github/boomers-analytics/www}}

---
```{r setup, include=FALSE}
# YOU WILL NEED TO CHANGE THE GRAPHICSPATH ABOVE IF YOU WANT YOUR OWN IMAGES!!!!!!!!!
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(pandoc)
library(ggplot2)
opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```

\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=2cm, height=2cm]{Schaumburg}
\end{minipage}
\hfill 
\begin{minipage}{0.3\textwidth}
\begin{center}
\textbf{\fontsize{24}{24}\selectfont `r params$pitcher`}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=3cm, height=2cm]{fllogo2}
\end{minipage}


\vspace{-7mm} 
\begin{center}
\textbf{\normalsize `r params$date` vs `r params$opponent`}
\end{center}
\vspace{-7mm} 

\begin{center}
\textbf{\normalsize Game Line}
\end{center}
\vspace{-6mm} 
```{r game stats, echo=FALSE, warning=FALSE }


kable(game_stats, format = "latex",  linesep = "") %>%
  kable_styling(latex_options = "HOLD_position", position = "center")%>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(ncol(game_stats), border_right = TRUE)
```
\vspace{-9mm} 
\begin{center}
\textbf{\normalsize Pitch Chracteristics}
\end{center}
\vspace{-6mm} 
```{r game summary,warning=FALSE,echo=FALSE}

game_summary_table  %>%
  kable(format = "latex",  linesep = "", label = "Game Summary") %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>%
  column_spec(1, bold = TRUE, border_left = TRUE, color = "white", 
              background = case_when(
                game_summary_table$Pitch == 'FB' ~ 'red',
                game_summary_table$Pitch == 'SI' ~ '#a34700',
                game_summary_table$Pitch == 'CT' ~ '#FFD700',
                game_summary_table$Pitch == 'CB' ~ '#228b22',
                game_summary_table$Pitch == 'SL' ~ '#33A8FF',
                game_summary_table$Pitch == 'CH' ~ '#E398F7',
                TRUE ~ 'black'
              )
  ) %>% 
  kable_pitch_metrics_cond_frmt_hi_low() %>%
  kable_pitch_metrics_cond_frmt_hot_cold() %>%
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(ncol(game_summary_table), border_right = TRUE) 
```
\vspace{-9mm} 

\begin{center}
\centering
\textbf{\normalsize Pitch Stats}
\end{center}
\vspace{-6mm} 

```{r usage and batted ball, echo=FALSE, warning=FALSE, results='asis', include = F}
knitr::kables(
  list(
    knitr::kable(
      pitch_usage_table, valign = 't', label = 'Pitch Usage'
    ) %>%
      column_spec(1, bold = TRUE, border_left =  TRUE, color = "white",
                  background = ifelse(game_summary_table$Pitch == 'FB', 'red',
                                      ifelse(game_summary_table$Pitch == 'SI', '#a34700',
                                             ifelse(game_summary_table$Pitch == 'CT', '#FFD700',
                                                    ifelse(game_summary_table$Pitch == 'CB', '#228b22',
                                                           ifelse(game_summary_table$Pitch == 'SL', '#33A8FF',
                                                                  ifelse(game_summary_table$Pitch == 'CH', '#E398F7',
                                                                         
                                                                         
                                                                         'black'))))))
      )%>%
      row_spec(row = 0, color = "white", background = "#12294b")%>%
      column_spec(ncol(pitch_usage_table), border_right = TRUE),
    
    knitr::kable(batted_ball,  valign = 't', label = 'Batted Ball') %>%
      column_spec(1, bold = TRUE, border_left =  TRUE, color = "white",
                  background = ifelse(game_summary_table$Pitch == 'FB', 'red',
                                      ifelse(game_summary_table$Pitch == 'SI', '#a34700',
                                             ifelse(game_summary_table$Pitch == 'CT', '#FFD700',
                                                    ifelse(game_summary_table$Pitch == 'CB', '#228b22',
                                                           ifelse(game_summary_table$Pitch == 'SL', '#33A8FF',
                                                                  ifelse(game_summary_table$Pitch == 'CH', '#E398F7',
                                                                         
                                                                         
                                                                         'black'))))))
      )%>%
      row_spec(row = 0, color = "white", background = "#12294b") %>%
      column_spec(ncol(batted_ball), border_right = TRUE)
  ), format = "latex" )   %>%
  kable_styling(latex_options = "HOLD_position")

```


```{r pitch stats,warning=FALSE,echo=FALSE}
pitch_usage_table  %>%
  kable(format = "latex",  linesep = "", label = "pitch stats") %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>%
  column_spec(1, bold = TRUE, border_left = TRUE, color = "white", 
              background = case_when(
                pitch_usage_table$Pitch == 'FB' ~ 'red',
                pitch_usage_table$Pitch == 'SI' ~ '#a34700',
                pitch_usage_table$Pitch == 'CT' ~ '#FFD700',
                pitch_usage_table$Pitch == 'CB' ~ '#228b22',
                pitch_usage_table$Pitch == 'SL' ~ '#33A8FF',
                pitch_usage_table$Pitch == 'CH' ~ '#E398F7',
                TRUE ~ 'black'
              )
  ) %>% 
  kable_pitch_stats_cond_frmt_hot_cold() %>%
  kable_pitch_stats_cond_frmt_hi_low() %>%
  
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(ncol(pitch_usage_table), border_right = TRUE) 

```
\vspace{-9mm} 

```{r, echo=FALSE, warning=FALSE, fig.width=7.8, fig.height = 3.4, fig.align='center'} 
# pitch_movement_plot
# arm_angle_plot
gridExtra::grid.arrange(pitch_movement_plot, arm_angle_plot, ncol = 2)
```
\vspace{-9mm} 

```{r, echo=FALSE, warning=FALSE, fig.width=7.8, fig.height = 2.9, fig.align='center'} 
gridExtra::grid.arrange(pvp_game_plot, pitch_dist_plot, ncol = 2)

# pvp_game_plot
# pitch_dist_plot
# rolling_stuff
```
\vspace{-1mm} 
\newpage
```{r, rhh usage and stats, echo=FALSE, warning=FALSE, include=FALSE}

if(nrow(usage_r)>0) {
  kable(usage_r, format = "latex")%>%
    kable_styling(latex_options = "HOLD_position",position = "left")%>%
    column_spec(1,  border_left = TRUE) %>%
    row_spec(row = 0, color = "white", background = "#12294b") %>%
    column_spec(ncol(usage_r), border_right = TRUE)
} else{"No data vs RHH available"}
if(nrow(usage_l)>0){
  kable(usage_l, format = "latex" )%>%
    kable_styling(latex_options = "HOLD_position",position = "left")%>%
    column_spec(1,  border_left = TRUE) %>%
    row_spec(row = 0, color = "white", background = "#12294b") %>%
    column_spec(ncol(usage_l), border_right = TRUE)
}else{"No data vs LHH available"}
```
\vspace{-2mm} 

\begin{center}
\begin{minipage}[t]{0.4\textwidth}
\centering
\textbf{\normalsize Pitch Usage vs Right}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\centering
\textbf{\normalsize Pitch Usage vs Left}
\end{minipage}
\end{center}
\vspace{-5mm} 

```{r Vs R & L,echo=FALSE,warning=FALSE }


knitr::kables(
  list(
    if(nrow(usage_r) >0){
      knitr::kable(
        usage_r, valign = 't', label = 'Pitch Usage'
      ) %>%
        column_spec(1, bold = TRUE, border_left =  TRUE, color = "white",
                    background = ifelse(game_summary_table$Pitch == 'FB', 'red',
                                        ifelse(game_summary_table$Pitch == 'SI', '#a34700',
                                               ifelse(game_summary_table$Pitch == 'CT', '#FFD700',
                                                      ifelse(game_summary_table$Pitch == 'CB', '#228b22',
                                                             ifelse(game_summary_table$Pitch == 'CH', '#E398F7',
                                                                    ifelse(game_summary_table$Pitch == 'SL', '#33A8FF',
                                                                           'black'))))))
        )%>%
        row_spec(row = 0, color = "white", background = "#12294b")%>%
        column_spec(ncol(usage_r), border_right = TRUE)},
    
    if(nrow(usage_l) >0){
      knitr::kable(usage_l,  valign = 't', label = 'Batted Ball') %>%
        column_spec(1, bold = TRUE, border_left =  TRUE, color = "white",
                    background = ifelse(game_summary_table$Pitch == 'FB', 'red',
                                        ifelse(game_summary_table$Pitch == 'SI', '#a34700',
                                               ifelse(game_summary_table$Pitch == 'CT', '#FFD700',
                                                      ifelse(game_summary_table$Pitch == 'CB', '#228b22',
                                                             ifelse(game_summary_table$Pitch == 'CH', '#E398F7',
                                                                    ifelse(game_summary_table$Pitch == 'SL', '#33A8FF',
                                                                           'black'))))))
        )%>%
        row_spec(row = 0, color = "white", background = "#12294b") %>%
        column_spec(ncol(usage_l), border_right = TRUE) }
  ), 
  format = "latex" )    %>%
  kable_styling(latex_options = "HOLD_position")
```
\vspace{-9mm} 

\begin{center}
\begin{minipage}[t]{0.4\textwidth}
\centering
\textbf{\normalsize Game Line vs Right}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\centering
\textbf{\normalsize Game Line vs Left}
\end{minipage}
\end{center}
\vspace{-6mm} 


```{r stats vs r and l, echo=FALSE, warning=FALSE}
knitr::kables(
  list(
    knitr::kable(
      stats_vs_r, valign = 't', label = 'Pitch Usage'
    ) %>%
      column_spec(1, bold = TRUE, border_left =  TRUE) %>%
      row_spec(row = 0, color = "white", background = "#12294b")%>%
      column_spec(ncol(stats_vs_r), border_right = TRUE),
    
    knitr::kable(
      stats_vs_l, valign = 't', label = 'Pitch Usage'
    ) %>%
      column_spec(1, bold = TRUE, border_left =  TRUE)%>%
      row_spec(row = 0, color = "white", background = "#12294b")%>%
      column_spec(ncol(stats_vs_l), border_right = TRUE)
  ), format = "latex" )    %>%
  kable_styling(latex_options = "HOLD_position")
```
\vspace{-6mm} 


```{r Pitch Location, echo=FALSE, warning=FALSE, fig.width=8.4,fig.height=3.25, position= 'center'} 
gridExtra::grid.arrange(plp_rhh, plp_lhh, ncol = 2)
```
\vspace{-10mm} 

\begin{center}
\textbf{\normalsize Situational Pitch Breakdown}
\end{center}
\vspace{-7mm} 
```{r breakdown, echo = F, warning = F, position='center', fig.height=3, fig.width=8, fig.align = 'center'}
breakdown
```
\vspace{-5mm} 
\begin{center}
\textbf{\normalsize Conditional Formatting Frontier League Percentile Guide}

Color coding compares to league average for each pitch type
\end{center}
\vspace{-7mm} 
```{r guide, echo = F, warning = F, position='center'}
colors_df_ex %>%
  slice(2) %>% 
  tibble::remove_rownames() %>%
  kable(format = "latex",  linesep = "", label = "pitch stats") %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>%
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(ncol(colors_df_ex), border_right = TRUE) %>%
  row_spec(row = 1, background = c('white', hot_cold), color = c('black','white', 'black','black','black','black','white','white')) # %>%
  # row_spec(row = 2, background = c('white', higher_lower), color = c('black','white', 'black','black','black','black','white','white'))
```