---
output:
  pdf_document: 
    keep_tex: false
geometry: margin=0.05in
 
header-includes:
 
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
 

---
```{r setup, include=FALSE}
#
library(webshot)
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(flextable)
library(pandoc)
library(ggplot2)
opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```

\begin{center}
\textbf{\LARGE `r params$pitcher` - `r params$date` vs `r params$opponent`}
\end{center}

\vspace{-7mm} 

\begin{center}
\textbf{\normalsize Game Line}
\end{center}
\vspace{-5mm} 
```{r game_summary_table and stats, echo=FALSE, warning=FALSE }

kable(game_stats, format = "latex",  linesep = "") %>%
  kable_styling(latex_options = "HOLD_position", position = "center")%>%
      column_spec(1, bold = TRUE, border_left = TRUE) %>%
      row_spec(row = 0, color = "black", background = "#FF5733") %>%
      column_spec(ncol(game_stats), border_right = TRUE)
```
\vspace{-9mm} 
\begin{center}
\textbf{\normalsize Pitch Chracteristics}
\end{center}
\vspace{-5mm} 
```{r pitch characteristics ,warning=FALSE,echo=FALSE}

# we again scale the colors manually to match the plots
game_summary_table %>%
  kable(format = "latex",  linesep = "", label = "Game Summary") %>%
  kable_styling(latex_options = "HOLD_position", position = "center") %>%
  column_spec(1, bold = TRUE, border_left = TRUE, color = "white", 
              background = ifelse(game_summary_table$Pitch == 'FB', 'red', 
                                  ifelse(game_summary_table$Pitch == 'SI', 'orange', 
                                         ifelse(game_summary_table$Pitch == 'CT', '#FFD700', 
                                                ifelse(game_summary_table$Pitch == 'CB', '#228b22', 
                                                       ifelse(game_summary_table$Pitch == 'SL', '#33A8FF', 
                                                              ifelse(game_summary_table$Pitch == 'CH', '#E398F7', 


                                         'black'))))))
              ) %>% 
  row_spec(row = 0, color = "black", background = "#FF5733") %>%
  column_spec(ncol(game_summary_table), border_right = TRUE) 
# data objects d1 and d2 are from the previous code chunk
```
\vspace{-8mm} 

\begin{center}
\begin{minipage}[t]{0.4\textwidth}
\centering
\textbf{\normalsize Pitch Usage}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\centering
\textbf{\normalsize Batted Ball Profile}
\end{minipage}
\end{center}
\vspace{-6mm} 

```{r pitch usage and batted ball, echo=FALSE, warning=FALSE}
knitr::kables(
  list(
    # the first kable() to change column names
    knitr::kable(
      pitch_usage_table, valign = 't', label = 'Pitch Usage'
      ) %>%
      column_spec(1, bold = TRUE, border_left =  TRUE, color = "white",
              background = ifelse(game_summary_table$Pitch == 'FB', 'red',
                                  ifelse(game_summary_table$Pitch == 'SI', 'orange',
                                         ifelse(game_summary_table$Pitch == 'CT', '#FFD700',
                                                ifelse(game_summary_table$Pitch == 'CB', '#228b22',
                                                       ifelse(game_summary_table$Pitch == 'SL', '#33A8FF',
                                                              ifelse(game_summary_table$Pitch == 'CH', '#E398F7',


                                         'black'))))))
              )%>%
      row_spec(row = 0, color = "black", background = "#FF5733")%>%
      column_spec(ncol(pitch_usage_table), border_right = TRUE),
    
    # the second kable() to set the digits option
    knitr::kable(batted_ball,  valign = 't', label = 'Batted Ball') %>%
      column_spec(1, bold = TRUE, border_left =  TRUE, color = "white",
              background = ifelse(game_summary_table$Pitch == 'FB', 'red',
                                  ifelse(game_summary_table$Pitch == 'SI', 'orange',
                                         ifelse(game_summary_table$Pitch == 'CT', '#FFD700',
                                                ifelse(game_summary_table$Pitch == 'CB', '#228b22',
                                                       ifelse(game_summary_table$Pitch == 'SL', '#33A8FF',
                                                              ifelse(game_summary_table$Pitch == 'CH', '#E398F7',


                                         'black'))))))
              )%>%
      row_spec(row = 0, color = "black", background = "#FF5733") %>%
      column_spec(ncol(batted_ball), border_right = TRUE)
  ), format = "latex" )    %>%
  kable_styling(latex_options = "HOLD_position")



# knitr::kable(game_stats,  valign = 't', label = 'Game Stats') %>%
#       column_spec(1, bold = TRUE, border_left = TRUE) %>%
#       row_spec(row = 0, color = "black", background = "#FF5733") %>%
#       column_spec(ncol(game_stats), border_right = TRUE)
#   ), format = "latex" )
```
\vspace{-5mm} 
```{r vb/hb plot and velo plot, echo=FALSE, warning=FALSE, fig.width=3,fig.height=3} 
pitch_movement_plot
pvp_game_plot
```
 \vspace{-5mm} 

\vspace{-2mm} 

```{r Pitch Location vs RHH and LHH, echo=FALSE, warning=FALSE, fig.width=4.15,fig.height=2.25, position= 'center'} 
if(nrow(usage_r)>0){
plp_rhh} else {"No data vs RHH available"}
if(nrow(usage_l)>0){
plp_lhh} else {"No data vs LHH available"}
```
\vspace{-5mm} 

\begin{center}
\begin{minipage}[t]{0.4\textwidth}
\centering
\textbf{\normalsize Pitch Usage vs Right}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\centering
\textbf{\normalsize Pitch Usage vs Left}
\end{minipage}
\end{center}
\vspace{-6mm} 

```{r usage vs R & L,echo=FALSE,warning=FALSE }


knitr::kables(
  list(
    # the first kable() to change column names
    if(nrow(usage_r) >0){
    knitr::kable(
      usage_r, valign = 't', label = 'Pitch Usage'
      ) %>%
      column_spec(1, bold = TRUE, border_left =  TRUE, color = "white",
              background = ifelse(game_summary_table$Pitch == 'FB', 'red',
                                  ifelse(game_summary_table$Pitch == 'SI', 'orange',
                                         ifelse(game_summary_table$Pitch == 'CT', '#FFD700',
                                                ifelse(game_summary_table$Pitch == 'CB', '#228b22',
                                                       ifelse(game_summary_table$Pitch == 'CH', '#E398F7',
                                                              ifelse(game_summary_table$Pitch == 'SL', '#33A8FF',
                                                                     'black'))))))
              )%>%
      row_spec(row = 0, color = "black", background = "#FF5733")%>%
      column_spec(ncol(usage_r), border_right = TRUE)},
    
    if(nrow(usage_l) >0){
    # the second kable() to set the digits option
    knitr::kable(usage_l,  valign = 't', label = 'Batted Ball') %>%
      column_spec(1, bold = TRUE, border_left =  TRUE, color = "white",
              background = ifelse(game_summary_table$Pitch == 'FB', 'red',
                                  ifelse(game_summary_table$Pitch == 'SI', 'orange',
                                         ifelse(game_summary_table$Pitch == 'CT', '#FFD700',
                                                ifelse(game_summary_table$Pitch == 'CB', '#228b22',
                                                       ifelse(game_summary_table$Pitch == 'CH', '#E398F7',
                                                              ifelse(game_summary_table$Pitch == 'SL', '#33A8FF',
                                                                     'black'))))))
              )%>%
      row_spec(row = 0, color = "black", background = "#FF5733") %>%
      column_spec(ncol(usage_l), border_right = TRUE) }
  ), 
  format = "latex" )    %>%
  kable_styling(latex_options = "HOLD_position")
```
\vspace{-8mm} 

\begin{center}
\begin{minipage}[t]{0.4\textwidth}
\centering
\textbf{\normalsize Game Line vs Right}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\centering
\textbf{\normalsize Game Line vs Left}
\end{minipage}
\end{center}
\vspace{-5mm} 


```{r stats vs r and l, echo=FALSE, warning=FALSE}
knitr::kables(
  list(
    # the first kable() to change column names
    knitr::kable(
      stats_vs_r, valign = 't', label = 'Pitch Usage'
      ) %>%
      column_spec(1, bold = TRUE, border_left =  TRUE)%>%
      row_spec(row = 0, color = "black", background = "#FF5733")%>%
      column_spec(ncol(stats_vs_r), border_right = TRUE),
    
    # the second kable() to set the digits option
    knitr::kable(
      stats_vs_l, valign = 't', label = 'Pitch Usage'
      ) %>%
      column_spec(1, bold = TRUE, border_left =  TRUE)%>%
      row_spec(row = 0, color = "black", background = "#FF5733")%>%
      column_spec(ncol(stats_vs_l), border_right = TRUE)
  ), format = "latex" )    %>%
  kable_styling(latex_options = "HOLD_position")



```
\vspace{-5mm} 
\newpage
\begin{center}
\textbf{\normalsize Situational Pitch Breakdown}
\end{center}
\vspace{-5mm} 

```{r situational breakdown, echo = F, warning = F, position='center', fig.height=3, fig.width=8}
breakdown
```

